### 2010-02-24 ChrisnaSections.tex
Sorta done with results; starting covariates talk.

    %% RESULTS:
    \subsection{Results}
    Below, in tables, lie our estimates for all of the Minnesota DNR's data from
    2003 and 2004.  Below each table is detailed commentary about the ability of
    the standard hierarchical model to convergence to the corresponding data.

@@

    2003's data worked relatively well with our model.  The presence of numerous
    observations that occur in the second and third days since the most recent
    snow event allows one of the more crucial assumptions of our hierarchical
    model -- that otter tracks laid on each day after a snow event are visible
    throughout the entire observation period and therefore, that it is more
    likely for an observer to detect a track on later days -- to be thoroughly
    tested.

@@

@@

    %%
    \subsection{The Effect of Plot Size}
    %%
    \subsection{All Plots vs. Every Other Plot}
    %%
    \subsection{How Important Are Our Covariates?}
    %%
    \subsection{Best Practices for Measuring Otter Occupancy}

\end{document}

>>>>

    %% RESULTS:
    \subsection{Results}
    Below, in tables, lie our estimates for all of the Minnesota DNR's data from
    2003 and 2004.  Below each table is detailed commentary about the ability of
    the standard hierarchical model to converge, given the corresponding data.

@@

    2003's data worked relatively well with the model.  The presence of numerous
    observations that occur in the second and third days since the most recent
    snow event allows one of the more crucial assumptions of our hierarchical
    model -- that otter tracks laid on each day after a snow event are visible
    throughout the entire observation period and therefore, that it is more
    likely for an observer to detect a track on later days -- to be thoroughly
    tested.  Most of the \(\psi\) and \(\theta\) estimates of 2003's data fall
    into ranges where our model is at its best, both with respect to convergence
    and to accurately estimating \(\psi\).

@@

    % Wow, this stuff SUCKS.
    As plot size increases, every estimated parameter tends to increase as well.
    Although the vast majority of these increases, even at the 1608m plot size,
    lie well within the 95\% confidence interval of the accompanying estimate at
    the 402m plot size, we believe that this trend makes sense.  Only one track
    detection within a plot is necessary to assign it a 1.  Therefore, once 402m
    plots are aggregated into 1608m plots, only one of the four 402m plots needs
    to be assigned a 1 in order for the entire 1608m plot to receive a 1.  The
    amount of correlation between 1's determines the increase in the proportion
    of 1's to the number of plots -- as the amount of correlation increases, the
    increase in the proportion decreases.

    We believe that this increase leads to higher \(\psi\) and \(\theta\)
    estimates because the potential for multiple otters to lay tracks within the
    same plot increases.  In southeastern Minnesota, most otters tolerate the
    presence of other otters in the areas they use most frequently, suggesting
    that they are neither solitary nor territorial \cite{Gorman2006}.  This is
    consistent with the noticeable but modest increase in \(\theta\) across plot
    % I have no idea how to explain this... :(.
    sizes for all three rivers.  However, estimates of \(\psi\) along the
    Whitewater and Zumbro Rivers remain constant, despite large increases in
    \(\theta\).

    % More detail, maybe?
    Similarly, the increases in estimates of \(p\) and \(E\) seem to result from
    the general increase of tracks laid per plot as the plot size grows.  As
    plot size grows, the influence of a 1 increases, regardless of whether an
    otter track or a track from a different animal was observed.

    Lastly, we decided to use the data from every plot even though we believe
    that, as a result, our data violates the assumption of independence between
    sites.  However, the model remains effective with spatially correlated data.
    Since the actual data is relatively sparse as it is, we consider the removal
    of half of it in order to preserve independence to be more harmful to the
    model than supplying it with correlated data.  Therefore, all estimates come
    from all of the data that we were given.

@@

    %% COVARIATES:
    \subsection{Covariates}
    To determine the relative importance of our covariates (the observer, the
    date, and the number of days since the most recent snow event), we ran the
    standard hierarchical model with \(E\) on simulated data with values of
    \(\psi\) and \(\theta\) similar to our estimates of \(\psi\) and \(\theta\)
    on 2003's data with varying numbers of observers, snow events, and
    observations after each snow event.

    \subsection{Best Practices for Measuring Otter Occupancy}

\bibliographystyle{alpha}
\bibliography{Bibliography}
\end{document}
